Numerous variables relating to 2016 election in 2021 US GSS^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis]

### 2022-03-20 outputs/paper/paper.Rmd
reference + discussion

@@

4) Clinton's vote is higher than trump's vote in this survey, which contradicts the election result of 2016, reader should keep in mind that this survey is more biased towards Clinton.

@@

In general, just as we expected by the trend we saw during our observation of the data, Hillary Clinton supporters were moved by improvement in social equality or welfare such as "Assistance to the Poor", "nation welfare", "nation education" and "Assistance to the other countries". On the other hand, Donald Trump supporters were interested by more conservative ideas that US is spending too much on the sessions above, and shows their support to Trump's slogan "Make America Great Again".

@@

## What was done in this paper?

## What is something that we learn about the world?
Even though the world has been trying hard for social welfare and equality, throughout this paper we have observed that there still exists disagreement within gender, race, wealth and age. U.S is just one example of this situation. If you extend your view to the world, you can observe this situation with no difficulties.

## what is left to learn or how should we proceed in the future?

## what are some weaknesses of what was done?

@@

>>>>

This report was created using `R` [@citeR] and its libraries `tidyverse` [@tidyverse], `dplyr` [@dplyr], were used to process and clean the data, and `ggplot` [@ggplot] `bookdown` [@bookdown] and `knitr` [@knitr] was used to format this report.

@@

@@

@@

## Summary
We have taken survey data to observe the trend in voters of 2016 presidential election of the United States. In general, just as we expected by the trend we saw during our observation of the data, Hillary Clinton supporters were moved by improvement in social equality or welfare such as "Assistance to the Poor", "nation welfare", "nation education" and "Assistance to the other countries". On the other hand, Donald Trump supporters were interested by more conservative ideas that US is spending too much on the sessions above, and shows their support to Trump's slogan "Make America Great Again".

## Disagreement Between Races, Gender, Ages, and Wealth
Even though the United States and many other countries around the world have been trying hard to improve social welfare and equality, throughout this paper we have observed that there still exists disagreement within gender, race, wealth and age, and this had massive impact on politics and was crucial factor on people's decision on who to vote for as the president. Despite the popular movements voicing for equality between genders, and races and such in recent years, it seems that the opinions of people in different groups, are very divided.

## Weaknesses and how we should proceed in the future
The data from U.S GSS contained large amount of data and information and the distribution of survey respondents were quite accurate in terms of race. However, there were significantly more females than males and significantly less people of ages in the 20s, 30s and 40s. It is important, especially for the topic of this paper, to have the data on the younger generation and how they view government policies and how it effects their vote for the presidential election.
To gain more knowledge in this trend of disagreement between people of different race, gender, age and wealth when it comes to the election, an additional survey could be made to answer WHY this disagreement is happening, by not just asking for their opinion but also asking about what they experience and witness. In the future, survey should be including questions that can allow us to better capture and understand the current trend in agreement and disagreement between different groups of people, it can allow us to study how it could effect the election in the future.

@@

U.S. Census Bureau quickfacts: United States. (n.d.), from https://www.census.gov/quickfacts/fact/table/US/PST045221
